---
output:
  md_document:
    variant: markdown_github
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-stuff}
if (!requireNamespace("pacman")) install.packages("pacman")
pacman::p_load(readr, dplyr, lubridate, RSQLite)
source("R/simulate_noise.R")
source("R/create_tag_db.R")
source("R/tag_finder.R")
```

## First pass at noise simulation and false positives

Very much a work in progress. But I seem to have `find_tags_unifile` running. However, I don't think that its defaults match what is currently run on the Motus server (`find_tags_motus`?) so I've attempted to fix that.

### Generate some noise

This works essentially by generating random time stamps over a period of user-specified `duration` (hours) at a user-specified `noise_rate` (noise pulses per second). One of the noisiest sites I'm aware of generates noise at about 80 pulses per second, so I'll use about 1/2 of that as a start. Like Denis's previous work, I by default assume all of these pulses will pass the tagfinder's frequency offset filter. That can be tweaked with the `fix_noise_freq` argument. The function currently generates an output `csv` that is ready to pass to `find_tags_unifile` via the `tag_finder` function down the road.

```{r noise}
# Simulate an hour of noise at 40 pulses/second
simulate_noise(duration = 1, noise_rate = 40, seed = 4242)
```

### Known tag database

I simply generated a composite `sqlite` file of ~ 260 registered tags from projects 4 and 140. I could not get `find_tags_unifile` to work with a `csv` of tag info, despite matching the field requirements as outlined in `R/find_tags_unifile.cpp`. But the `sqlite` worked and was easy enough to generate. By default it is output to `Data/tag_db.sqlite`.

```{r tabdb}
create_tag_db(sqlite_dir = "Data/tag_databases/")
```

### Running the tagfinder from R

Running `find_tags_unifile` with its defaults is as straightforward as making a `system` call specifying only the known tag database and the simulated SensorGnome noise data, capturing the output, and reading the resulting `csv`.

```{r tagfinder-defaults}
command <- paste("find_tags_unifile", "Data/tag_db.sqlite", "Data/simulated_sg_noise.csv")
tf <- system(command, intern = TRUE)
tf <- readr::read_csv(tf)
nrow(tf)
head(tf)
```

In looking through the [tagfinder repo](https://github.com/MotusWTS/find_tags), it appears that `find_tags_unifile` was compiled with slightly different defaults than the current(?) `find_tags_motus` running on the Motus server. So I wrapped `find_tags_unifile` to expose the main tag finder parameters of interest, and attempt to set them to match the defaults of `find_tags_motus`. The most noticeable default change is changing `pulses_to_confirm` from 4 (default in `find_tags_unifile`) to 8 (`find_tags_motus`). This require a run length of at least 2 for the false positive to be logged. The function that does this is `tag_finder`.

```{r use-tfmotus-defaults}
tf_motus <- tag_finder("Data/tag_db.sqlite", "Data/simulated_sg_noise.csv")
nrow(tf_motus)
head(tf)
```

For funsies, let's simulate 4 hours of very noisy data and see what comes out by default...

```{r noisy, cache = TRUE}
simulate_noise(4, noise_rate = 100, seed = 2020, out = "Data/very_noisy.csv")
# Fair warning: 3+ minutes on a relatively decent machine
system.time(tf_noisy <- tag_finder("Data/tag_db.sqlite", "Data/very_noisy.csv"))
nrow(tf_noisy)

tf_noisy_g <- group_by(tf_noisy, fullID, run.id) %>%
  summarize(ts = min(ts),
            runLen = max(pos.in.run))
table(tf_noisy_g$runLen)
```

